Notes on Design and Implementation of Anglican

### 2015-07-17 paper/paper.tex
design outline in progress
editorial

Because of the checkpoints, Anglican programs must allow the
inference algorithm to intervene, recording information and
affecting control flow. This can be implemented through coroutines/
cooperative multitasking, parallel execution/preemptive
multitasking and shared memory, as well as through explicit
maintenance of program continuations at checkpoints. Clojure is
a functional language, and continuation-passing style (CPS)
transformation is a well-developed technique in the area of
functional languages. Implementing a variant of CPS
transformation seemed to be the most flexible and lightweight
option --- any other form of concurrency would put a higher burden
on the underlying runtime (JVM) and the operating system.
Consequently, Anglican has been implemented as a CPS-transformed
computation with access to continuations in probabilistic
checkpoints. Anglican `compiler', represented by a set of
functions in the \texttt{anglican.trap} namespace, accepts a
Clojure subset and transforms it into a variant of CPS
representation, which allows inference algorithms to intervene
in the execution flow at probabilistic checkpoints.

@@

>>>>

Because of the checkpoints, Anglican programs must allow the
inference algorithm to step in, recording information and
affecting control flow. This can be implemented through coroutines/
cooperative multitasking, parallel execution/preemptive
multitasking and shared memory, as well as through explicit
maintenance of program continuations at checkpoints. Clojure is
a functional language, and continuation-passing style (CPS)
transformation is a well-developed technique in the area of
functional languages. Implementing a variant of CPS
transformation seemed to be the most flexible and lightweight
option --- any other form of concurrency would put a higher burden
on the underlying runtime (JVM) and the operating system.
Consequently, Anglican has been implemented as a CPS-transformed
computation with access to continuations in probabilistic
checkpoints. Anglican `compiler', represented by a set of
functions in the \texttt{anglican.trap} namespace, accepts a
Clojure subset and transforms it into a variant of CPS
representation, which allows inference algorithms to intervene
in the execution flow at probabilistic checkpoints.

@@

Operational semantic of Anglican queries is different from that
of Clojure code, therefore queries must be called through
inference algorithms, rather than `directly'.
